Testing Rate of Change Transition models

### 2023-05-25 minos/testing/rate_of_change_testing.Rmd
Cosmetic changes to the rate_of_change_testing.Rmd notebook, and modified the spaghetti_plot() function in utils_validation_vis.R to allow for saving and automatically name handover plots as such in filenames

@@

## Spaghetti Plots

### hh_income

```{r}
income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
income.spag.base

income.spag.raw <- spaghetti_plot(raw.dat, 'hh_income')
income.spag.raw
```

#### Comparison

The base spaghetti plot doesn't look very good actually... I think I need a version using the previous models so I'll do a baseline run and save the data somewhere for testing purposes.

```{r}
old.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/mean_regen_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
old.dat <- do.call(rbind, lapply(old.files, read.csv))
# remove dead people
old.dat <- old.dat %>%
  filter(alive != 'dead')

income.spag.base <- spaghetti_plot(base.dat, 'hh_income')
income.spag.base

income.spag.old <- spaghetti_plot(old.dat, 'hh_income')
income.spag.old
```

### SF_12_MCS

```{r}
sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
sf12.spag.base

sf12.spag.raw <- spaghetti_plot(raw.dat, 'SF_12')
sf12.spag.raw
```
Need to remove missing values.

#### Comparison

```{r}
sf12.spag.base <- spaghetti_plot(base.dat, 'SF_12')
sf12.spag.base

sf12.spag.old <- spaghetti_plot(old.dat, 'SF_12')
sf12.spag.old
```

## Violin Plots

### hh_income

```{r}
income.violin.base <- violin_plot(base.dat, 'hh_income')
income.violin.base

income.violin.raw <- violin_plot(raw.dat, 'hh_income')
income.violin.raw
```

### SF12

```{r}
sf12.violin.base <- violin_plot(base.dat, 'SF_12')
sf12.violin.base

sf12.violin.raw <- violin_plot(raw.dat, 'SF_12')
sf12.violin.raw
```

>>>>

# Spaghetti Plots

## Data
```{r}
old.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/mean_regen_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
old.dat <- do.call(rbind, lapply(old.files, read.csv))
# remove dead people
old.dat <- old.dat %>%
  filter(alive != 'dead')

new.files <- list.files('/home/luke/Documents/WORK/MINOS/PREVIOUS_OUTPUTS/diff_income_sf12/', pattern='[0-9]{4}.csv', full.names = TRUE)
new.dat <- do.call(rbind, lapply(new.files, read.csv))
new.dat <- new.dat %>%
  filter(alive != 'dead')
```

```{r}
spaghetti_plot(old.dat, 'hh_income')
spaghetti_plot(new.dat, 'hh_income')
spaghetti_plot(raw.dat, 'hh_income')
```

## SF_12_MCS

```{r}
spaghetti_plot(old.dat, 'SF_12')
spaghetti_plot(new.dat, 'SF_12')
spaghetti_plot(raw.dat, 'SF_12')
```

# Violin Plots

```{r}
violin_plot(old.dat, 'hh_income')
violin_plot(new.dat, 'hh_income')
violin_plot(raw.dat, 'hh_income')
```

```{r}
violin_plot(old.dat, 'SF_12')
violin_plot(new.dat, 'SF_12')
violin_plot(raw.dat, 'SF_12')
```

@@
